%-------------------------
% Resume in Latex
% Author : Zakir Muqueet
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Zakir Muqueet} \\ \vspace{1pt}
  \small US Citizen $|$ \small 817-404-2936 $|$ \href{mailto:x@x.com}{\underline{Muqueetz@Outlook.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/Zakir-Muqueet}} $|$
    \href{https://github.com/...}{\underline{https://github.com/MuqueetZakir}}
\end{center}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    % University and Degree
    \resumeSubheading
      {University of Texas at Arlington}{Arlington, TX}
      {Bachelor of Science in Computer Engineering}{\textit{Expected Graduation: May 2026}}
    
    % Concentrations
    \resumeSubheading
      {Concentrations}{}{Systems Programming and Robotics/Digital Hardware}{}
     \small{\item{
      \textbf{Relevant Coursework}\\ \textit{Data Structures \& Algorithms, Computer Organization \& Programming, Machine Learning, Circuit Analysis, Digital-Logic Design, Object-Oriented. Embedded Systems}}
}
  \resumeSubHeadingListEnd
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL, JavaScript, HTML/CSS, Python} \\
     \textbf{Frameworks}{: React, Node.js, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib}
    }}
     \end{itemize}

%-----------PROJECTS-----------


\section{Projects}
    \resumeSubHeadingListStart
            
      \resumeProjectHeading
        {\textbf{AVR Snake Game} $|$ \emph{C, AVR, LCD, EEPROM, Arduino Libraries}}         
          \resumeItemListStart
            \resumeItem{Developed a snake game on an AVR microcontroller with an LCD display and EEPROM to store high scores.}
            \resumeItem{Implemented game mechanics including snake movement, food placement, score tracking, and collision detection with obstacles.}
            \resumeItem{Integrated sound effects for actions such as eating food and game-over events using a buzzer.}
            \resumeItem{Designed a custom LCD interface with animations and real-time updates for score and high score display.}
        \resumeItemListEnd
          
      \resumeProjectHeading
        {\textbf{PyCleanUp} $|$ \emph{Python, Bash, macOS Utilities, Homebrew, npm}}
          \resumeItemListStart
          \resumeItem{Developed a Python script to clean and optimize system performance by removing caches, logs, and\temporary files.}
          \resumeItem{Automated the deletion of cache files from macOS, Chrome, JetBrains, Xcode, and other development tools to free up space.}
          \resumeItem{Integrated options for dry-run execution, color-coded logging, and error handling using bash trap and cleanup functions.}
          \resumeItem{Implemented support for updating and cleaning package managers like Homebrew and npm, ensuring optimal system efficiency.}
      \resumeItemListEnd
    
      \resumeProjectHeading
        {\textbf{Stock Prediction App} $|$ \emph{Python, Streamlit, yFinance, Prophet, Plotly}}
          \resumeItemListStart
          \resumeItem{Developed a web application to predict stock prices using historical data and machine learning with the Prophet library.}
          \resumeItem{Integrated the yFinance API to fetch real-time stock data for analysis and forecasting.}
          \resumeItem{Implemented interactive visualizations with Plotly to display raw data, forecasted trends, and components of the predictions.}
          \resumeItem{Enhanced user experience with Streamlit, allowing users to select stocks and adjust prediction parameters dynamically.}
      \resumeItemListEnd
    
      \resumeProjectHeading
        {\textbf{Blackjack Game} $|$ \emph{Java, OOP}}
          \resumeItemListStart
          \resumeItem{Developed a console-based Blackjack game using Java, incorporating object-oriented principles such as enums for suits and ranks, and classes for cards and players.}
          \resumeItem{Implemented a scoring system that dynamically calculates the player's and dealer's hand values, including logic for handling Aces as 1 or 11.}
          \resumeItem{Added features for user interaction, allowing players to hit or stand, with input validation for commands and game actions.}
          \resumeItem{Included file handling to save game results, enabling players to store their game history in a user-specified file.}
      \resumeItemListEnd
    
 \end{itemize}

%-------------------------------------------
\end{document}

